\documentclass[12pt]{report}


\usepackage{url}
\usepackage{xspace}
\usepackage{fancybox}
\usepackage{cuthesis}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{csquotes}
\usepackage{multirow}
\usepackage{pdflscape}
\usepackage{subfigure}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{adjustbox}
\usepackage{array}
\usepackage{mathtools}
\usepackage[titletoc]{appendix}
\usepackage[tikz]{bclogo}
\usepackage[framemethod=tikz]{mdframed}
\usepackage{lipsum}
\usepackage[many]{tcolorbox}


	
\usepackage{caption}



\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}



	\newtcolorbox{myboxii}[1][]{
	breakable,
	title=#1,
	colback=white,
	colbacktitle=white,
	coltitle=black,
	fonttitle=\bfseries,
	bottomrule=0pt,
	toprule=0pt,
	leftrule=3pt,
	rightrule=3pt,
	titlerule=1pt,
	arc=0pt,
	outer arc=0pt,
	colframe=black,
	enlarge top by=0.5cm
}

\linespread{1.6}

\author{Sultan Wehaibi}
\title {On the Relationship Between Self-Admitted Technical Debt and Software Quality}
\degree{Master of Applied Science in Software Engineering}
\dept  {Computer Science and Software Engineering}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% define commands for frequently used words or phrases
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\SATD}{self-admitted technical debt\xspace}
\newcommand{\ie}{i.e.\xspace}
\newcommand{\eg}{e.g.\xspace}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% define commands for your RQs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\chapterIIIrqi}{\textbf{RQ1 - Do technical debt files have more bugs? Do files become more buggy after the introduction of technical debt?}}
\newcommand{\chapterIIIrqii}{\textbf{RQ2 - Do technical debt related changes tend to introduce future bugs?}}
\newcommand{\chapterIIIrqiii}{\textbf{RQ3 - Do technical debt related changes tend to be more difficult?}}


\newcommand{\chapterIVrqI}{\textbf{RQ1: Do god and SATD files have more defects than non-god and non-SATD files?}}

\newcommand{\chapterIVrqII}{\textbf{RQ2: Do god- and SATD-related changes introduce future defects?}}

\newcommand{\chapterIVrqIII}{\textbf{RQ3: Are god- and SATD-related changes more difficult than non-god and non-SATD changes?}}

\newcommand{\chapterIVrqIV}{\textbf{RQ4: Is there an overlap between comment- and metric-based technical debt?}}

\definecolor{dartmouthgreen}{rgb}{0.05, 0.5, 0.06}
\newcommand{\sultan}[1]{\textcolor{RoyalBlue}{{\it [Sultan: #1]}}}
\newcommand{\emad}[1]{\textcolor{ForestGreen}{{\it [Emad: #1]}}}
\newcommand{\todo}[1]{\textcolor{WildStrawberry}{\textbf{[#1]}}}
\newcommand{\incomplete}[1]{\textcolor{dartmouthgreen}{\textbf{[#1]}}}
\newcommand{\revision}{\textbf{\colorbox{red}{[REVISION]}}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% define command to create a conclusion box to answer your RQs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\conclusionbox}[1]{%
    \vspace{6mm}
    \framebox[0.95\textwidth][c]{%
        \parbox[b]{0.92\textwidth}{%
            {\it #1}
        }
    }
    \vspace{6mm}
}


\makeatletter
\renewcommand{\@chapapp}{}% Not necessary...
\newenvironment{chapquote}[2][2em]
{\setlength{\@tempdima}{#1}%
	\def\chapquote@author{#2}%
	\parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
	\itshape}
{\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
\makeatother


\begin{document}

\begin{abstract}
	
	
%Technical debt refers to incomplete or temporary workarounds that allow us to speed up software development in the short term at the cost of paying a higher price later on. Recently, studies have shown that technical debt can be detected from source code comments, referred to as "self-admitted technical debt." Researchers have examined the detection, classification and removal of self-admitted technical debt. However, to date, no empirical evidence has been compiled to assess the impact of self-admitted technical debt on software quality.

Developers settle for a non-optimal solution under pressure to meet deadlines and quotas despite the potential pitfalls that might ensue at later stages in development, which has been referred to as ``technical debt." And like its financial analogue, if not carefully monitored and mediated, technical debt can compromise the very project it was intended to expedite. Several approaches have been proposed to aid developers in tracking the technical debt they incur. Traditionally, developers have relied on metric-based approaches, which use static analysis tools to identify technical debt based on thresholds defined on object-oriented metrics, e.g. code smells. Another technique, pioneered in a recent study, leverages source code comments to detect (self-admitted) technical debt. Therefore, in this thesis we use empirical studies to examine how self-admitted technical debt and code smells (God Classes) relate to software quality.

Preliminarily, we examine the relationship between \SATD and software quality for five open-source projects. To measure this, we take into account three criteria commonly associated with quality: (i) on the file level, the relationship between defects and \SATD (SATD); (ii) on the change level, the potential of SATD to introduce future defects and (iii) the complexity SATD changes impose on the system. The results of our study indicate that: (i) SATD files tend to have less defects than non-SATD files and (ii) SATD changes make the system less susceptible to future defects than non-SATD changes do, though (iii) SATD changes are more difficult to execute.

Until the advent of SATD, god classes were used to detect technical debt, and though others have studied the impact of metric-based approaches on software quality, this work has been limited to a small number of systems. Therefore, we conduct an extensive investigation that compares the relationship between both approaches and software quality on a larger number of projects. We assess how code smells---in particular, god classes (metric-based approach)---and SATD (comment-based approach) are associated with software quality by determining: (i) whether god and SATD files have more defects than non-god and non-SATD files, (ii) whether god and SATD changes induce future defects at a higher rate than non-god and non-SATD changes, (iii) whether god and SATD changes are more difficult to perform than non-god and non-SATD changes and (iv) how much the metric- and comment-based approaches to technical debt file identification overlap. Our results indicate that: (i) neither god nor SATD files are correlated with defects, (ii) introduction of future defects is higher for god- and SATD-related changes, (iii) god- and SATD-related changes are more difficult to perform and (iv) the metric-comment technical debt file overlap ranges from 11\% to 34\%.

Overall, our study indicates that although technical debt---whether measured by the SATD or god classes---may have negative effects, these do not include file-level defects. Rather, the detriments of technical debt are its tendencies to introduce future defects at an elevated rate and to make the system more difficult to change in the future. In terms of detection methods, our work advocates implementing both the comment- and metric-based approaches to maximize the sources of technical debt identified.


\end{abstract}



\begin{acknowledgments}

The first and last of my thanks go to Allah for His abundant blessings of knowledge, health, patience, endurance, motivation and willingness to change for the better.\\ \par

I am grateful to my supervisor, Dr. Emad Shihab, for his insightful comments and constructive feedback on the earlier drafts of this thesis. I also appreciate that he encouraged me to attend conferences that ultimately informed much of my research, as I had opportunities to discuss the state of the art with those on the forefront of innovation in the field. Emad, I cannot thank you enough for your tireless support and sharing your expertise with me throughout the last two years.\\
\par
I am indebted to my thesis examiners, Dr. Weiyi Shang and Dr. Juergen Rilling, for taking the time to read my thesis and offering constructive revisions and valuable suggestions, which were incorporated into the final version. I also thank the other faculty members of the Department of Computer Science and Software Engineering, each of whom had a hand in lightening my journey and providing some moments of welcome levity.\\ \par

I am fortunate to count myself among my colleagues, who are some of the brightest researchers I have had the pleasure of collaborating with: Rabe Abdalkareem, Suhaib Mujahid, Davood Mazinanian, Jin Fu, Kundi Yao, Omid Sarbishei and everyone else who broadened my vision by offering their unique perspectives on my work.\\ \par

Throughout this journey, I have enjoyed the love and support of many of my closest friends: John Meyer, St\'{e}phane Leclerc, Connor Phoennik, Wael El-Dweesh, Haitham Al-Bisaily Osamah Al-Wabel, Ammar Al-Washali, Toshiki Hirao, and Michael Shu. I could never have made it this far in my academic career without a cast of people so invested in my future success.\\ \par

To my mom, dad and siblings---I am sincerely grateful for the values you instilled in me which have served me well this far and will no doubt carry over into a career as accomplished and satisfying as yours. You have taught me to love and give always, neither expecting immediate returns nor returns at all. As my dad used to tell me, nobody owes you anything---life is what you make it. \\ \\ \\ \\ \\ \\ \\ \\ \\ \\

\begin{chapquote}{Malcom X}
	``The future belongs to those who prepare for it today."
\end{chapquote}

	
\end{acknowledgments}




\begin{dedication}
	\begin{flushright}
	%always think critically and be skeptical of what you hear.\\
	\textit{To my mom, my dad, and my brother Ahmed.}
	\end{flushright}

\end{dedication}


\begin{thought}
\vspace*{\fill}
\begin{center}
	\begin{minipage}{.8\textwidth}
			\begin{chapquote}{Sultan}
			``Always think critically and be skeptical of what you hear." 
		\end{chapquote}
	\end{minipage}
\end{center}
\vfill 
\end{thought}

\begin{publications}

The following publications are related to this thesis:

\begin{enumerate}

\item \textbf{Sultan Wehaibi}, Emad Shihab and Latifa Guerrouj. Examining the Impact of Self-admitted Technical Debt on Software Quality. In \textit{Proceedings of the 23rd IEEE International Conference on Software Analysis, Evolution, and Reengineering (SANER’16)}, 10 pages, 2015. [Chapter 3]

%\item \textbf{Sultan Wehaibi}, Emad Shihab. TBA. In \textit{IEEE Transactions on Software Engineering}, XX pages, XXXXX revision submitted XXX 20XX. [Chapter 4] 

\end{enumerate}

\end{publications}

\chapter{Introduction}
\label{introduction}
\input{introduction.tex}


\chapter{Background \& Related Work}
\label{literature_review}
\input{literature_review.tex}

\chapter{Examining the Relationship Between Self-Admitted Technical Debt and Software Quality}
\label{chapter3}
\input{chapter3.tex}

\chapter{Comparing the Relationship Between Comment- Versus Metric-Based Technical Debt and Software Quality}
\label{chapter4}
\input{chapter4.tex}

\chapter{Summary, Contributions and Future Work}
\label{conclusion}
\input{conclusion.tex}


\begin{appendices}
	\label{appendix}
	\input{appendix.tex}
\end{appendices}

\addcontentsline{toc}{chapter}{Bibliography}
\bibliography{bibliography.bib}  
\bibliographystyle{alpha}
\end{document}